Queue Aware Precoder Design for Space Frequency Resource Allocation

### 2014-07-10 Report/simulation_distributed.tex
ver_0.0.1
16.48 Jul 4 2014
modified for KKT MMSE

Fig. \ref{fig-d-1} also compares the performance of the iterative algorithm for \ac{JSFRA} scheme via \ac{MSE} reformulation using the \ac{KKT} conditions discussed in Section \ref{sec-4.3}. The performance is inferior compared to the other algorithms due to the violation in the assumptions made in the algorithm design \textit{i.e}, \me{Q_k \gg t_k}. Since in this case, we are comparing the \me{q = 1} case, the queue condition \me{Q_k \gg t_k} needs to be satisfied in order to remove the absolute operator from the expression in \eqref{eqn-9.1a} to form \eqref{kkt-mse-1.1}. The total number of backlogged packets after the each iteration reduces monotonically in all cases and converges to the points closer to the centralized solution \me{\chi = 33} bits. As seen in Fig. \ref{fig-d-1}, the \ac{ADMM} approach provides better convergence compared to the primal approach in the initial phase due to the quadratic penalty term included in the objective, which gets pronounced initially due to the large deviation between the assumed and the actual interference across the coordinating \acp{BS}.
\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\columnwidth]{NewFigures/distribute_queue-1}
\caption{Queue deviation}
\label{fig-d-1.1}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\columnwidth]{NewFigures/distribute_sum_rate-1}
\caption{Sum rate performance}
\label{fig-d-1.2}
\end{subfigure}
\caption[short]{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,12,1 \rbrace} model}
\label{fig-d-1}
\end{figure*}

@@

The performance of the joint \ac{Q-WSRM} scheme discussed in the Section \ref{sec-3.1} performs slightly worse than (\me{\approx \, 2} bits) the \ac{JSFRA} scheme in reducing the number of queued packets, even though the performance were similar in Table \ref{tbl-1}. As stated earlier, the joint \ac{Q-WSRM} scheme and the \ac{JSFRA} scheme with the exponent \me{q = 1} performs the same when the number of queued packets are identical for all the users. In this case, the joint \ac{Q-WSRM} becomes the sum rate maximization problem which is equivalent to the greedy \me{q=1} \ac{JSFRA} scheme. In the current scenario, since the number of queued packets are different for the users, the performance of the \ac{JSFRA} scheme is better due to its greedy resource allocation. It can be seen from Fig. \ref{fig-d-2}, that the \ac{KKT} based approach provides inferior result in the queue minimization perspective as compared with the sum rate plot. The performance degradation is due to the unconstrained rate increase for the users beyond their actual number of queued packets available to transmit. Since the objective uses the norm-\me{1} minimization, the \ac{KKT} solution is not optimal unless the queues are far greater than the transmission rate available for each user. The number of queued packets are initialized in a way to analyze the effect of the unconstrained behavior in the \ac{KKT} scheme.
\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{NewFigures/distributed_queue_plot_1}
\caption{Queue deviation}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{NewFigures/distributed_sum_rate_plot_1}
\caption{Sum rate performance}
\end{subfigure}
\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,3,12,2 \rbrace} model}
\label{fig-d-2}
\end{figure*}

The performance of the \ac{MSE}-\ac{KKT} scheme is shown in comparison with the other schemes discussed so far in Fig. \ref{fig-d-3}. It can be seen that the \ac{KKT} based approach performs similar to the optimization problem given in \eqref{eqn-9}, which is solved using the solver \cite{grant2008cvx}. In the two norm case, the objective is differentiable and hence can be differentiable for any number of queued packets as compared to the one norm case requiring larger queue sizes in order to drop the absolute function occurring in the norm function. The performance of the closed form solution using the \ac{KKT} solution achieves similar performance without allocating rates beyond the available queued packets. In order to bring out the performance difference, one norm objective plot is also provided in Fig. \ref{fig-d-3} providing better reduction in the number of queued packets in the current transmission slot.
Fig. \ref{fig-d-3}
\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{queues_6_3_12}
\caption{Queue deviation}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{rate_6_3_12}
\caption{Sum rate performance}
\end{subfigure}
\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,1 \rbrace} model}
\label{fig-d-3}
\end{figure*}

>>>>

Fig. \ref{fig-d-1} also compares the performance of the iterative algorithm for \ac{JSFRA} scheme via \ac{MSE} reformulation using the \ac{KKT} conditions discussed in Section \ref{sec-4.3}. The performance is inferior compared to the other algorithms due to the violation in the assumptions made in the algorithm design \textit{i.e}, \me{Q_k \gg t_k}. Since in this case, we are comparing the \me{q = 1} case, the queue condition \me{Q_k \gg t_k} needs to be satisfied in order to remove the absolute operator from the expression in \eqref{eqn-9.1a} to form \eqref{kkt-mse-1.1}. The total number of backlogged packets after the each iteration reduces monotonically in all cases and converges to the points closer to the centralized solution \me{\chi = 33} bits. As seen in Fig. \ref{fig-d-1}, the \ac{ADMM} approach provides better convergence compared to the primal approach in the initial phase due to the quadratic penalty term included in the objective, which gets pronounced initially due to the large deviation between the assumed and the actual interference across the coordinating \acp{BS}.
\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\columnwidth]{NewFigures/distribute_queue-1}
\caption{Queue deviation}
\label{fig-d-1.1}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\columnwidth]{NewFigures/distribute_sum_rate-1}
\caption{Sum rate performance}
\label{fig-d-1.2}
\end{subfigure}
\caption[short]{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace} model}
\label{fig-d-1}
\end{figure*}

@@

The performance of the joint \ac{Q-WSRM} scheme discussed in the Section \ref{sec-3.1} performs slightly worse than (\me{\approx \, 2} bits) the \ac{JSFRA} scheme in reducing the number of queued packets, even though the performance were similar in Table \ref{tbl-1}. As stated earlier, the joint \ac{Q-WSRM} scheme and the \ac{JSFRA} scheme with the exponent \me{q = 1} performs the same when the number of queued packets are identical for all the users. In this case, the joint \ac{Q-WSRM} becomes the sum rate maximization problem which is equivalent to the greedy \me{q=1} \ac{JSFRA} scheme. In the current scenario, since the number of queued packets are different for the users, the performance of the \ac{JSFRA} scheme is better due to its greedy resource allocation. It can be seen from Fig. \ref{fig-d-2}, that the \ac{KKT} based approach provides inferior result in the queue minimization perspective as compared with the sum rate plot. The performance degradation is due to the unconstrained rate increase for the users beyond their actual number of queued packets available to transmit. Since the objective uses the \me{\ell_1} minimization, the \ac{KKT} solution is not optimal unless the queues are far greater than the transmission rate available for each user. The number of queued packets are initialized in a way to analyze the effect of the unconstrained behavior in the \ac{KKT} scheme.
\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{NewFigures/distributed_queue_plot_1}
\caption{Queue deviation}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{NewFigures/distributed_sum_rate_plot_1}
\caption{Sum rate performance}
\end{subfigure}
\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,3,12,2 \rbrace} model}
\label{fig-d-2}
\end{figure*}

The performance of the \ac{MSE}-\ac{KKT} scheme is shown in comparison with the other schemes discussed so far in Fig. \ref{fig-d-3}. It can be seen that the \ac{KKT} based approach performs similar to the optimization problem given in \eqref{eqn-9}, which is solved using the solver \cite{grant2008cvx}. In the \me{\ell_2} case, the objective is differentiable and hence can be differentiable for any number of queued packets as compared to the \me{\ell_1} case requiring larger queue sizes in order to drop the absolute function occurring in the norm operator. The performance of the closed form solution using the \ac{KKT} solution achieves similar performance without allocating rates beyond the available queued packets. In order to bring out the performance difference, \me{\ell_1} objective plot is also provided in Fig. \ref{fig-d-3} providing better reduction in the number of queued packets in the current transmission slot.
Fig. \ref{fig-d-3}
\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{fig-7}
\caption{Queue deviation}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{fig-8}
\caption{Sum rate performance}
\end{subfigure}
%\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,1 \rbrace} model}
\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 4,2,12,1 \rbrace} model}
\label{fig-d-3}
\end{figure*}

### 2014-07-10 Report/system_model.tex
modified for KKT MMSE

In this paper we adopt linear beamforming technique at \acp{BS}. Specifically, the data symbols \me{d_{l,k,n}} for  user \me{k} on the \me{l^\mathrm{th}} spatial stream over the sub-channel \me{n} is multiplied with the beamformer \me{\mvec{m}{l,k,n} \in \mathbb{C}^{N_T \times 1}} for transmission.   In order to detect  multiple spatial streams at the receiver, a receive beamforming vector \me{\mvec{w}{l,k,n}} is employed at each user. Consequently, the received data symbol corresponding to the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n^\mathrm{th}} at user $k$ is given by
\begin{equation}\label{eqn-1}
\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n}
\end{equation}
where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} with rank \me{L = \min(N_R,N_T)} is the channel between the \ac{BS} \me{b} and  user \me{k} on the sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for the user \me{k} on the \me{n^\mathrm{th}} sub-channel and \me{l^\mathrm{th}} spatial stream. Assuming  \me{||\mvec{w}{l,k,n}||_{2}^{2} = 1} and independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
\begin{equation}\label{eq:SINR}
\gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^\herm \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{N_0 + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}.
\end{equation}
With the infinite buffer model assumption, let \me{Q_k} be the number of backlogged packets which are destined for the user \me{k} at a given scheduling instant. The queue dynamics of the user \me{k} are modeled using the Poisson arrival process with the average packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets/bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets or bits arriving for the user \me{k} at the \me{{i}^\mathrm{th}} instant. The total number of queued packets at the \me{{(i+1)}^\mathrm{th}} instant for the user \me{k}, represented by \me{Q_k(i+1)}, follows
\begin{equation}
Q_k(i+1) = \Big [ Q_k(i) - t_k(i) \Big ]^+ + \lambda_k(i),
\label{eqn-2a}
\end{equation}
where \me{[x]^+ \equiv \max{ \lbrace x,0  \rbrace}} and \me{t_k} denotes the transmission in bits for user \me{k}. For a \ac{MIMO} \ac{OFDM} system,
\begin{equation}
t_k(i) = \sum_{n = 1}^N \, \sum_{l = 1}^L \, t_{l,k,n}(i),
\end{equation}
where \me{t_{l,k,n}} denotes the transmitted bits over \me{\ith{l}} spatial stream on the \me{\ith{n}} sub-channel. The maximum rate achieved over the \me{(l,n)} space-frequency resource is given by \me{\log_2(1 + \gamma_{l,k,n})}\footnote{assuming Gaussian signaling} for the \ac{SINR} of \me{\gamma_{l,k,n}}. Note that the units of \me{t_k} and \me{Q_k} are in bits defined per channel use.

>>>>

In this paper we adopt linear beamforming technique at \acp{BS}. Specifically, the data symbols \me{d_{l,k,n}} for  user \me{k} on the \me{l^\mathrm{th}} spatial stream over the sub-channel \me{n} is multiplied with the beamformer \me{\mvec{m}{l,k,n} \in \mathbb{C}^{N_T \times 1}} for transmission.   In order to detect  multiple spatial streams at the receiver, a receive beamforming vector \me{\mvec{w}{l,k,n}} is employed at each user. Consequently, the received data symbol corresponding to the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n^\mathrm{th}} at user $k$ is given by
\begin{equation}\label{eqn-1}
\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n}
\end{equation}
where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} with rank \me{L = \min(N_R,N_T)} is the channel between the \ac{BS} \me{b} and  user \me{k} on the sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for the user \me{k} on the \me{n^\mathrm{th}} sub-channel and \me{l^\mathrm{th}} spatial stream. Assuming  \me{||\mvec{w}{l,k,n}||_{2}^{2} = 1} and independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
\begin{equation}\label{eq:SINR}
\gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^\herm \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{N_0 + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}.
\end{equation}
With the infinite buffer model assumption, let \me{Q_k} be the number of backlogged packets which are destined for the user \me{k} at a given scheduling instant. The queue dynamics of the user \me{k} are modeled using the Poisson arrival process with the average packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets/bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets or bits arriving for the user \me{k} at the \me{{i}^\mathrm{th}} instant. The total number of queued packets at the \me{{(i+1)}^\mathrm{th}} instant for the user \me{k}, represented by \me{Q_k(i+1)}, follows
\begin{equation}
Q_k(i+1) = \Big [ Q_k(i) - t_k(i) \Big ]^+ + \lambda_k(i),
\label{eqn-2a}
\end{equation}
where \me{[x]^+ \equiv \max{ \lbrace x,0  \rbrace}} and \me{t_k} denotes the transmission in bits for user \me{k}. For a \ac{MIMO} \ac{OFDM} system,
\begin{equation}
t_k(i) = \sum_{n = 1}^N \, \sum_{l = 1}^L \, t_{l,k,n}(i),
\end{equation}
where \me{t_{l,k,n}} denotes the transmitted bits over \me{\ith{l}} spatial stream on the \me{\ith{n}} sub-channel. The maximum rate achieved over the \me{(l,n)} space-frequency resource is given by \me{\log_2(1 + \gamma_{l,k,n})}\footnote{Gaussian signaling assumption} for the \ac{SINR} of \me{\gamma_{l,k,n}}. Note that the units of \me{t_k} and \me{Q_k} are in bits defined per channel use.

### 2014-07-10 Report/wsrm_formulation.tex
Updated on 16.47:Jul-2
modified for KKT MMSE

The problem now is to find optimal transmit beamformers for a given set of linear receivers which is a challenging task. We note that for fixed $\mvec{w}{l,k,n}$, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint. Thus, the difficulty is due to the non-convexity in \eqref{eqn-6.2}. To arrive at a tractable formulation, we adopt the \ac{SCA} method to handle \eqref{eqn-6.2} by replacing the original non-convex constraint by the series of convex constraints. Note that the function \me{f(\tilde{\mbf{u}}_{l,k,n})} in \eqref{eqn-6.2} is convex for fixed \me{\mvec{w}{l,k,n}} since it is in fact the ratio between a quadratic form (of \me{\mvec{m}{l,k,n}}) over an affine function (of \me{\beta_{l,k,n}}) \cite{boyd2004convex}. According to the \ac{SCA} method, we relax \eqref{eqn-6.2} to a convex constraint in each iteration of the iterative procedure. Since \me{f(\tilde{\mbf{u}}_{l,k,n})} is convex, a concave approximation of \eqref{eqn-6.2} can be easily found by considering the first order approximation of \me{f(\tilde{\mbf{u}}_{l,k,n})} around the current operation point. For this purpose, let the real and imaginary component of the complex number \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}} be represented by
\begin{subeqnarray} \label{eqn-wsrm-expr}
p_{l,k,n} &\triangleq& \Re \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}}, \\
q_{l,k,n} &\triangleq& \Im \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}},
\end{subeqnarray}
and hence \me{f(\tilde{\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}. Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notation and not the newly introduced optimization variables. In CVX \cite{grant2008cvx}, for example,  we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `\emph{expression}' qualifier. Suppose that the current value of \me{p_{l,k,n}} and \me{q_{l,k,n}} at a specific iteration are \me{\tilde{p}_{l,k,n}} and \me{\tilde{q}_{l,k,n}}, respectively. Using the first order Taylor approximation around the local point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, we can approximate \eqref{eqn-6.2} by the following linear inequality constraint
\begin{equation}
\label{eqn-8}
2 \dfrac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \dfrac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) + \dfrac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \dfrac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
\end{equation}
In summary, for the fixed linear receivers, the \ac{JSFRA} problem to find transmit beamformers is shown by
\begin{IEEEeqnarray}{rCl}\label{eqn-9}
\underset{\substack{\gamma_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \\
\text{subject to} & \quad & \beta_{l,k,n} \geq  N_0 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \IEEEyessubnumber \label{eqn-9.1c} \\
& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-9.1d} \\
& \quad & \text{and } \eqref{eqn-8} \IEEEyessubnumber \label{eqn-9.1e}.
\end{IEEEeqnarray}

The proposed algorithm is referred as \ac{QM} \ac{JSFRA} scheme with a sum power constraint which is outlined in Algorithm \ref{algo-1}. The iterative procedure repeats until the improvement on the objective is less than a predetermined tolerance parameter or the maximum number of iterations is reached. Instead of initializing \me{\tilde{\mbf{u}}_{l,k,n}} arbitrarily to a feasible point, transmit precoders can also be initialized with any feasible point \me{\tilde{\mbf{m}}_{l,k,n}}, which is then used to find \me{\tilde{\mbf{u}}_{l,k,n}} in an efficient manner as briefed in Algorithm \ref{algo-1}. In Algorithm \ref{algo-1}, the \ac{SCA} iterations are carried until convergence or for maximum of \me{I_{\max}} iterations for the optimal \me{\mbf{w}_{l,k,n}} receive beamformers and the outer iterations are for the convergence of the number of queued bits, which is limited by the maximum of \me{J_{\max}} iterations.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=0}, \me{j=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
 update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}}\;
 \Repeat{Queue convergence or \me{j \geq J_{\max}}}{
 \Repeat{\ac{SCA} convergence or \me{i \geq I_{\max}}}{
 solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9} \;
 update the constraint set \eqref{eqn-8} with \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} using \eqref{eqn-wsrm-expr} with the precoders \me{\mvec{m}{l,k,n}} obtained from the previous step \;
 $i = i + 1$ \;
 }
 update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}} \;
 $j = j + 1$ \;
 }
 \caption{Algorithm of \acs{JSFRA} scheme}
 \label{algo-1}
\end{algorithm}

@@

In the proposed solution, we replaced \eqref{eqn-6.2} by a convex constraint using the first order approximation, which basically means that we do not solve the problem exactly. According to the traditional \ac{BCDM}, we need to solve a sub problem when fixing a set of variables to the global optimum to ensure the convergence to a stationary point. If we just approximate the objective, then the convergence is guaranteed \cite{razaviyayn2013unified}. In our case, we solve the sub problem inexactly, so the convergence proof of \ac{BCDM} does not apply to our problem. In this problem, we used alternating optimization with \ac{SCA} method, which provides monotonic convergence since the objective is improved at each step \textit{i.e} \me{f^{(i)} \geq f^{(i+1)}}, assuming \me{f^{(i)}} is the objective function at the \me{i^\mathrm{th}} \ac{SCA} iteration. For a fixed receive beamformers, the problem is guaranteed to converge to a \ac{KKT} point at each \ac{SCA} iteration as discussed in \cite{tran2012fast}. Now, by alternating the transmit and the receive precoders, we perform \ac{BCDM}, which provides monotonic convergence of the objective. Since the \ac{SCA} method is also considered in our problem, the convergence is not straight forward. We can only speculate the convergence based on the monotonicity of the objective values. Since receive beamformers are based on the \ac{MMSE} objective, it improves the objective value for each update, providing a monotonic increase in the objective value.

>>>>

The problem now is to find optimal transmit beamformers for a given set of linear receivers which is a challenging task. We note that for fixed $\mvec{w}{l,k,n}$, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint. Thus, the difficulty is due to the non-convexity in \eqref{eqn-6.2}. To arrive at a tractable formulation, we adopt the \ac{SCA} method to handle \eqref{eqn-6.2} by replacing the original non-convex constraint by the series of convex constraints. Note that the function \me{f(\tilde{\mbf{u}}_{l,k,n})} in \eqref{eqn-6.2} is convex for fixed \me{\mvec{w}{l,k,n}} since it is in fact the ratio between a quadratic form (of \me{\mvec{m}{l,k,n}}) over an affine function (of \me{\beta_{l,k,n}}) \cite{boyd2004convex}. According to the \ac{SCA} method, we relax \eqref{eqn-6.2} to a convex constraint in each iteration of the iterative procedure. Since \me{f(\tilde{\mbf{u}}_{l,k,n})} is convex, a concave approximation of \eqref{eqn-6.2} can be easily found by considering the first order approximation of \me{f(\tilde{\mbf{u}}_{l,k,n})} around the current operation point. For this purpose, let the real and imaginary component of the complex number \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}} be represented by
\begin{subeqnarray} \label{eqn-wsrm-expr}
p_{l,k,n} &\triangleq& \Re \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}}, \\
q_{l,k,n} &\triangleq& \Im \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}},
\end{subeqnarray}
and hence \me{f(\tilde{\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}. Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notation and not the newly introduced optimization variables. In CVX \cite{grant2008cvx}, for example,  we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `\emph{expression}' qualifier. Suppose that the current value of \me{p_{l,k,n}} and \me{q_{l,k,n}} at a specific iteration are \me{\tilde{p}_{l,k,n}} and \me{\tilde{q}_{l,k,n}}, respectively. Using the first order Taylor approximation around the local point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, we can approximate \eqref{eqn-6.2} by the following linear inequality constraint
\begin{equation}
\label{eqn-8}
2 \dfrac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \dfrac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) + \dfrac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \dfrac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
\end{equation}
In summary, for the fixed linear receivers, the \ac{JSFRA} problem to find transmit beamformers is shown by
\begin{IEEEeqnarray}{rCl}\label{eqn-9}
\underset{\substack{\gamma_{l,k,n},p_{l,k,n},q_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \\
\text{subject to} & \quad & \beta_{l,k,n} \geq  N_0 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \IEEEyessubnumber \label{eqn-9.1c} \\
& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-9.1d} \\
& \quad & \text{and } \eqref{eqn-8} \IEEEyessubnumber \label{eqn-9.1e}.
\end{IEEEeqnarray}

The proposed algorithm is referred as \ac{QM} \ac{JSFRA} scheme with a per \ac{BS} power constraint which is outlined in Algorithm \ref{algo-1}. The iterative procedure repeats until the improvement on the objective is less than a predetermined tolerance parameter or the maximum number of iterations is reached. Instead of initializing \me{\tilde{\mbf{u}}_{l,k,n}} arbitrarily to a feasible point, transmit precoders can also be initialized with any feasible point \me{\tilde{\mbf{m}}_{l,k,n}}, which is then used to find \me{\tilde{\mbf{u}}_{l,k,n}} in an efficient manner as briefed in Algorithm \ref{algo-1}. In Algorithm \ref{algo-1}, the \ac{SCA} iterations are carried until convergence or for maximum of \me{I_{\max}} iterations for the optimal \me{\mbf{w}_{l,k,n}} receive beamformers and the outer iterations are for the convergence of the number of queued bits, which is limited by the maximum of \me{J_{\max}} iterations.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=0}, \me{j=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
 update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}}\;
 \Repeat{Queue convergence or \me{j \geq J_{\max}}}{
 \Repeat{\ac{SCA} convergence or \me{i \geq I_{\max}}}{
 solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9} \;
 update the constraint set \eqref{eqn-8} with \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} using \eqref{eqn-wsrm-expr} with the precoders \me{\mvec{m}{l,k,n}} obtained from the previous step \;
 $i = i + 1$ \;
 }
 update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}} \;
 $j = j + 1$ \;
 }
 \caption{Algorithm of \acs{JSFRA} scheme}
 \label{algo-1}
\end{algorithm}

@@

In the proposed solution, we replaced \eqref{eqn-6.2} by a convex constraint using the first order approximation, which basically means that we do not solve the problem exactly. According to the traditional \ac{BCDM}, we need to solve a sub problem when fixing a set of variables to the global optimum to ensure the convergence to a stationary point. If we just approximate the objective, then the convergence is guaranteed \cite{razaviyayn2013unified}. In our case, we solve the sub problem inexactly, so the convergence proof of \ac{BCDM} does not apply to our problem. In this problem, we used alternating optimization with \ac{SCA} method, which provides monotonic convergence since the objective is improved at each step \textit{i.e} \me{f^{(i)} \geq f^{(i+1)}}, assuming \me{f^{(i)}} is the objective function at the \me{i^\mathrm{th}} \ac{SCA} iteration. For a fixed receive beamformers, the problem is guaranteed to converge to a \ac{KKT} point at each \ac{SCA} points as discussed in \cite{marks1978technical}. Now, by alternating the transmit and the receive precoders, we perform \ac{BCDM}, which provides monotonic convergence of the objective. Since the \ac{SCA} method is also considered in our problem, the convergence is not straight forward. We can only speculate the convergence based on the monotonicity of the objective values. Since receive beamformers are based on the \ac{MMSE} objective, it improves the objective value for each update, providing a monotonic increase in the objective value.
